Estimating duration in the presence of misclassification

### 2023-12-11 cis-imperfect-testing.tex

% Discussion and interrogation of the data led me to
I hypothesised that the reason for the unexpectedly high number of single positive episodes (compared to simulation) was the presence of false negatives results.
There are two strands of evidence supporting this hypothesis.
First, it is well known that PCR testing can return false negatives  (see \cref{E-biology-data:sec:PCR}); I explicitly include them in the viral load model of \cref{E-ATACCC}.
Intermittent negatives (described in  \cref{E-biology-data:sec:PCR}) show that they occur within the CIS.
Second, adjusting the simulation to include false negatives can reproduce both the CIS data more faithfully and exhibits the same issues when estimating the duration distribution (see \cref{imperf-test:fig:sim-single-pos}).
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/sim-single-positive-episodes}
  \todo[inline]{Figure showing estimates without false negatives}
  \caption[Estimating survival using CIS data assuming perfect testing]{Estimating the survival function using CIS data and the model of \cref{E-perf-test} gives implausibly short estimates.}
  \label{imperf-test:fig:sim-single-pos}
\end{figure}

>>>>

% Discussion and interrogation of the data led me to
I hypothesised that the reason for the unexpectedly high number of single positive episodes (compared to simulation) was the presence of false negatives results.
There are two strands of evidence supporting this hypothesis.
First, it is well known that PCR testing can return false negatives  (see \cref{E-biology-data:sec:PCR}); I explicitly include them in the viral load model of \cref{E-ATACCC}.
Intermittent negatives (described in  \cref{E-biology-data:sec:PCR}) show that they occur within the CIS.
Second, adjusting the simulation to include false negatives can reproduce both the CIS data more faithfully and exhibits the same issues when estimating the duration distribution (see \cref{imperf-test:fig:sim-single-pos}).
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/sim-single-positive-episodes}
  \caption[Single positive episodes in CIS simulation]{%
    Proportion of detected episodes which have a single positive episode.
    y-axis is the number of simulations, out of 1000, with the indicated proportion.
    The CIS data is shown as a vertical line.
    Simulation methodology is explained in \cref{E-perf-test:sec:simulation-study}, with false negatives included as described in \cref{imperf-test:sec:simulate}.
  }
  \label{imperf-test:fig:sim-single-pos}
\end{figure}
